---
title: "ggplot2"
output: html_document
date: "2022-08-29"
---

```{r}
library(ggplot2)
```

# 1. Produce a bar graph shaded by cut
```{r}
plot <- ggplot(data = diamonds,mapping = aes(clarity)) +
  geom_bar(aes(fill = factor(cut)), alpha = 0.3)

plot
```


# 2. Produce a density plot of price filled by cut
```{r}
plot2 <- ggplot(data=diamonds, mapping=aes(price)) +
  geom_density(aes(fill = factor(cut)), alpha = 0.3)

plot2
```

# 3. Produce a box plot of price broken down by color
```{r}
plot3 <- ggplot(data=diamonds, mapping = aes(y=price)) +
  geom_boxplot(aes(fill = factor(color))) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

plot3

```

# 4. Adding a faceted breakdown by clarity 
```{r}
ggplot(data = diamonds, mapping = aes(y=price)) +
  geom_boxplot(aes(fill = color)) +
  facet_wrap(~ clarity, ncol = 2)
  
```



# Produce a plot with a regression line 
## What was learned from this?
What was learned from this is that there is almost a linear correlation between price and carrat. It looks like the price is higher when the carrat is an integer and not between two integers. 
```{r}
plot <- ggplot(diamonds, mapping =  aes(x =carat,y=price))+
  geom_point()

plot + stat_smooth(method = "lm",
                   formula = y~x,
                   geom = "smooth")
```

