---
title: "Project_1"
output: html_document
date: "2022-09-13"
---
```{r}
library(ggplot2)
```



## Item 1:
## a
```{r}
values <- c(45,77,20,19,101,120,212)
celcius <- (5/9)*(values - 32)
celcius
```
##b
```{r}


convertTemp <- function(farenheit)
  {
  return ((5/9)*(farenheit - 32))
  }
values <- c(45,77,20,19,101,120,212)

###Either of these will do
sapply(values,convertTemp)
convertTemp(values)
```
## c and d
```{r}
set.seed(440)

uniform_random_distribution <- runif(100)
scaled_uniform_random_distribution <- scale(runif(100))
hist(scaled_uniform_random_distribution)
####
####
random_normal_distribution  <- rnorm(100)
scaled_random_normal_distribution <- scale(rnorm(100))
hist(scaled_random_normal_distribution)
```


## Item 2:
###### Getting the census data and visualizing it by Race/Ethnicity, Median income, and year
```{r}
census <-read.csv("../DATA/census_data.csv")

census$race <-factor(census$race, levels = c("White","Black","Asian","Hispanic"))
table(census$race)
```
```{r}
census$year <- factor(census$year,  levels= c(2016,2017,2018,2019))
ggplot(data=census,aes(x= race,y= Income, fill = year)) +
  geom_bar(stat="identity", position= position_dodge2())
```


## Item 3:
```{r}
diamonds$cut <- as.numeric(diamonds$cut)
diamonds$color<- as.numeric(diamonds$color)
diamonds$clarity <- as.numeric(diamonds$clarity)

set.seed(440)
sampled <- sample(1:length(diamonds$carat), 0.8*length(diamonds$carat), replace = FALSE)

diamond_train <- diamonds[sampled,]
diamond_test <- diamonds[-sampled,]
```

## Making the first model
##### Using carat, color, clarity, cut to predict the price:
```{r}
diamond_model_1 <- lm(data=diamond_train, price ~ carat + color + clarity + cut)
model_1_summary <- summary(diamond_model_1)
model_1_summary
```

```{r}
model_1_predict <-predict(object = diamond_model_1, diamond_test)
resid_model_1 <- diamond_test$price - model_1_predict
### Chose degree of freedom based on 6 predictors and one intercept = 7
### Length of test is 10'788
model_1_RSE <- sqrt(sum(resid_model_1^2)/10781)
var(model_1_predict)/var(diamond_test$price)
```

##### RSE train: 1234
##### RSE test: 1241
##### When assessing the fit, the model (R2 = .915)  predicts that there is high correlation between the actual and predicted variables. When using the RSE 2 to 1 rule, the RSE test perfectly is within the value of 2*Train. Therefore, this is a good model. 
##### (Asses compared to the RSE 2 to 1  rule)

## Making the second model
##### Using carat, color, clarity, cut, x, y, z to predict the price:
```{r}
diamond_model_2 <- lm(data=diamond_train, price ~ carat + color + clarity + cut +  x + y + z)
model_2_summary <- summary(diamond_model_2)
model_2_summary
```

```{r}
model_2_predict <- predict(object = diamond_model_2, diamond_test)

resid_model_2 <- diamond_test$price - model_2_predict


### Chose degree of freedom based on 9 predictors and one intercept = 10
### Length of test is 10'788
model_2_RSE <- sqrt(sum(resid_model_2^2)/10778)
var(model_2_predict)/var(diamond_test$price)

```

##### Train RSE: 1217
##### Test RSE: 1230
##### When assessing the fit, the model (R2 = .916)  predicts that there is high correlation between the actual and predicted variables. When using the RSE 2 to 1 rule, the RSE test perfectly is within the value of 2*Train. Therefore, this is a good model. 
##### (Asses compared to the RSE 2 to 1  rule)