---
title: "Project_2"
output: html_document
date: "2022-10-06"
---
```{r}
library(tidyverse)
library(MASS)
library (naivebayes)
library(caret)
```


# Item 4:
##### What are the predictors for atherosclerosis without cardiac catheterizatoin
```{r}
heart_data <- read.csv("../../DATA/heart.csv")
```
## A.
### Lets explore the data
```{r}
dim(heart_data)
colnames(heart_data)
```
### lets look at the relationships between cholesterol and output in a box plot
```{r}
heart_data$output <-factor(heart_data$output, levels =  c(0,1))
ggplot(data = heart_data,aes(y=chol))+
  geom_boxplot(aes(fill =output))

ggplot(data = heart_data,aes(y=fbs))+
  geom_boxplot(aes(fill =output))

summary(heart_data$chol)
summary(heart_data$fbs)
```
##### The results of the cholesterol indicates that approximatelly 75% of patients have serum cholesterol greater than 200 (normal). A good statistic would be to look at the amount of people who have high cholesterol and an output of 1 and vice versa
##### The range between the first quartile and the third quartile is 90 - 114, indicating that there are at least 50% of patients that have a blood sugar in the normal range of 80-120.

## B.
### Splitting the data
```{r}
set.seed(440)
n <- nrow(heart_data)
heart_sample <- sample(1:n,n*0.6,replace = FALSE)

heart_train <- heart_data[heart_sample,]
heart_test <- heart_data[-heart_sample,]
```
### Logistic Regression
```{r}

reg_heart_model <- glm(output ~ . ,data = heart_train, family = binomial)
reg_heart_summary <- summary(reg_heart_model)
reg_heart_summary
```

```{r}

```

```{r}
#plot(x = , y = reg_heart_model$fitted.values)
```

### LDA
```{r}
lda_heart_model <- lda(output ~., data = heart_train)
lda_heart_model
```
```{r}
lda_heart_predict <- predict(object = lda_heart_model, data = heart_test)
```
```{r}
plot(lda_heart_model)
```


### Naive Bayes
```{r}
bayes_heart_model <- naive_bayes(output ~., data = heart_train)
print(bayes_heart_model)
summary(bayes_heart_model)
plot(bayes_heart_model)
```

```{r}
bayes_heart_predict_prob <- predict(bayes_heart_model, type = "prob")
bayes_heart_predict_class <- predict(bayes_heart_model, type = "class")
```
```{r}
t <- table("predict" = bayes_heart_predict_class, "truth" = heart_train$output)

sum(diag(t)) / nrow(heart_train) # Accuraccy
```
```{r}
bayes_heart_test_predict_class <- predict(object = bayes_heart_model, newdata = heart_test, type = "class")
```
```{r}
confusionMatrix(bayes_heart_test_predict_class, reference=heart_test$output)
```
```{r}
library (pROC)
y <- as.numeric(heart_test$output)
x <- as.numeric(bayes_heart_test_predict_class)
grad_roc = roc(y ~ x, plot = TRUE, print.auc = TRUE, 
               auc.polygon=FALSE, legacy.axes=TRUE)
```




