---
title: "Project_2_item2"
output: html_document
date: "2022-10-06"
---
# Item 2:
## A.
```{r}
white_wine <- read.csv("../../DATA/winequality-white.csv")
n <- nrow(white_wine)
white_sample <- sample(1:n, n*0.8, replace = FALSE)

white_train <- white_wine[white_sample,]
white_test <- white_wine[-white_sample,]

set.seed(440)

white_model <- lm(quality ~ fixed_acidity+residual_sugar+total_sulfur_dioxide+ pH+ alcohol, data = white_train)

white_model_summary <- summary(white_model)
white_model_summary

```
## B.
```{r}
white_wine_predict <- predict(object = white_model, white_test)
white_wine_resid <- white_wine_predict - white_test$quality
### 5 predictors plus one intercept --> 6 degrees of freedom
### 980 rows in white wine - 6 = 974
white_wine_test_RSE <- sqrt(sum(white_wine_resid^2)/974)
var(white_wine_predict)/var(white_test$quality)
```
##### Test: 0.7855
##### Train: 0.79
##### According to the "2 to 1" rule, this is a good model. However, according to the R2 of 0.19, this would not be as good of a model. 

## C.
##### Projecting the red wine dataset onto the white wine dataset; Using the white wine model to predict the values of the red wine dataset. The residuals are based off of the red wine dataset
```{r}
red_wine <- read.csv("../../DATA/winequality-red.csv")
red_wine_predict <- predict(object = white_model,data = red_wine)
####Need to order this
red_wine_resid <- red_wine_predict - red_wine$quality
### 5 predictors plus one intercept --> 6 degrees of freedom
### 1599 rows in red wine - 6 = 1593
#red_wine_RSE <- sqrt(sum(white_wine_resid^2)/1593)
#var(red_wine_predict)/var(red_wine$quality)

```

## D.
##### Poor (0) wine is quality <= 4, Excellent(1) wine is quality >= 8, Eliminate all wine that is inbetween
```{r}
quality <- function(x){
  if (x <= 4){
    x <- 0
  }
  else if(x >= 8){
    x <- 1
  }
  else{
    x <- NA
  }
}

white_wine$classifier <- sapply(white_wine$quality,quality)
white_wine <- na.omit(white_wine)

quality_factor<- factor(white_wine$classifier, levels = c(0,1), labels = c("Bad", "Good"))
table(quality_factor)
```

```{r}
quality2 <- glm(classifier ~ fixed_acidity+residual_sugar+total_sulfur_dioxide+ pH+ alcohol, data = white_wine, family = binomial)
summary(quality2)
```
```{r}
plot(x=white_wine$classifier,y=quality2$fitted.values, main = "Fitted Values Plot")
plot(x=white_wine$fixed_acidity,y=quality2$fitted.values, main = "Fitted Values Plot")
plot(x=white_wine$residual_sugar,y=quality2$fitted.values, main = "Fitted Values Plot")
plot(x=white_wine$total_sulfur_dioxide,y=quality2$fitted.values, main = "Fitted Values Plot")
plot(x=white_wine$pH,y=quality2$fitted.values, main = "Fitted Values Plot")
plot(x=white_wine$alcohol,y=quality2$fitted.values, main = "Fitted Values Plot")

```

```{r}
logitR2 <- 1 - (quality2$deviance/quality2$null.deviance)
logitR2
```
```{r}
criteria <- 0.5
predWine <- ifelse (quality2$fitted.values > criteria, "Yes", "No") #We can set this
```
```{r}
t = table (predWine, "Truth" = quality_factor)
t
library (caret)
#confusionMatrix(t, positive = "Yes")  #"Yes" is you get the loan
```

```{r}
library(pROC)
par(pty="s") # forces plot to be square as ROC plots should be!
logit_roc = roc(white_wine$quality ~ quality2$fitted.values, 
                plot = TRUE, axis = TRUE, xlim=c(1,0), ylim=c(0,1),
                legacy.axes = TRUE, print.auc = TRUE, grid=TRUE,
                identity=TRUE, add = FALSE)
```

