---
title: "Project_2"
output: html_document
date: "2022-10-06"
---
```{r}
library(tidyverse)
```


# Item 4:
##### What are the predictors for atherosclerosis without cardiac catheterizatoin
```{r}
heart_data <- read.csv("../../DATA/heart.csv")
```
## A.
### Lets explore the data
```{r}
dim(heart_data)
colnames(heart_data)
```
### lets look at the relationships between cholesterol and output in a box plot
```{r}
heart_data$output <-factor(heart_data$output, levels =  c(0,1))
ggplot(data = heart_data,aes(y=chol))+
  geom_boxplot(aes(fill =output))

ggplot(data = heart_data,aes(y=fbs))+
  geom_boxplot(aes(fill =output))

summary(heart_data$chol)
summary(heart_data$fbs)
```
##### The results of the cholesterol indicates that approximatelly 75% of patients have serum cholesterol greater than 200 (normal). A good statistic would be to look at the amount of people who have high cholesterol and an output of 1 and vice versa
##### The range between the first quartile and the third quartile is 90 - 114, indicating that there are at least 50% of patients that have a blood sugar in the normal range of 80-120.

## B.
### Splitting the data
```{r}
n <- nrow(heart_data)
heart_sample <- sample(1:n,n*0.7,replace = FALSE)

heart_train <- heart_data[heart_sample,]
heart_test <- heart_data[-heart_sample,]
```
### Regression
```{r}
reg_heart_model <- lm(output ~ . ,data = heart_train)
reg_heart_summary <- summary(reg_heart_model)

```
### LDA
```{r}

```
### Naive Bayes
```{r}

```
### KNN
```{r}

```




